Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

    In previous work, we introduced an algorithm inspired by the biological
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    In a previous work \cite{Felix-Saul2022} we used to generate a new random
    set of solutions, with the cost of losing all evolution knowledge.

@@

        The strategy we describe in this paper use an elite set, that includes
        the historically best-found candidate solutions to take
        advantage of the historical evolution. Our goal is for the offspring to
        be somewhat close to the best individuals of the Elite.
        We use the golden ratio to compute the distance between new individuals in the population, making
        an improved distribution. % Why is better? Explain. - M

>>>>

    In previous work, we introduced an algorithm inspired by the biological
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart).

    % Maybe you do it later, but explain what is a restart precisely 
    In a previous work \cite{Felix-Saul2022} we used to generate a new random
    set of solutions, with the cost of losing all evolution knowledge.

@@

        The strategy we describe in this paper use an elite set, that includes
        the historically best-found candidate solutions to take
        advantage of the historical evolution. Our goal is for the offspring to
        be somewhat close to the best individuals of the Elite.
        We use the golden ratio to compute the distance between new individuals in the population, making
        an improved distribution. We can consider our strategy an improvement 
        over other alternatives because of the findings of our latter experiments.
